Statistical Mechanics Assignment One

### 2016-04-14 stat_mech/latex/a1.tex
Add new statmech stuff.

\title{Classical Mechanics Assignment 9}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

\begin{align*}
  \tau \frac{\partial\phi}{\partial t} &= -\frac{\delta G}{\delta \phi}\\
  \\
  \frac{\partial \tilde{u}}{\partial t} &= \nabla^2 u + F\frac{\partial \phi}{\partial t}\\
  \\
  G(\phi_{i,j}) &= V(\phi_{i,j}) + \frac{\delta^2(\nabla\phi_{i,j})^2}{2}\\
\end{align*}

>>>>

\title{Statistical Mechanics Assignment One}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

\section{Problem One: Adiabatic Ideal Gas}
\textbf{a.)}
First we calculate the final temperature of the gas, given $V_i, V_f$ and $T_i$:

\begin{align*}
  P_iV_i^\gamma &= nRT_iV_i^{\gamma-1}\\
  nRT_iV_i^{\gamma-1} &= nRT_fV_f^{\gamma-1}\\
  T_f &= T_i\left(\frac{V_i}{V_f}\right)^{\gamma-1}
\end{align*}

\textbf{b.)}
If $dS=0$, then $dQ/T=0$ and so $dU = -pdV$. We use this as another route for finding $T_f$ in
terms of $V_i, V_f$ and $T_i$:

\begin{align*}
  dU &= -pdV = C_vdT\\
  -\frac{RT}{V}dV &= C_vdT \hspace{2cm}\mbox{Molar specific heat, so n=1}\\
  -R\int_{V_i}^{V_f}\frac{1}{V}dV &= C_v\int_{T_i}^{T_f}\frac{1}{T}dT\\
  -R\ln\left(\frac{V_f}{V_i}\right) &= C_v\ln\left(\frac{T_f}{T_i}\right)\\
  -\frac{C_p-C_v}{C_v}\ln\left(\frac{V_f}{V_i}\right) &= \ln\left(\frac{T_f}{T_i}\right)\\
  \ln\left(\frac{V_f}{V_i}\right)^{1-\gamma} &= \ln\left(\frac{T_f}{T_i}\right)\\
  \left(\frac{V_f}{V_i}\right)^{1-\gamma} &= \frac{T_f}{T_i}\\
  T_f &= T_i\left(\frac{V_f}{V_i}\right)^{1-\gamma} = T_i\left(\frac{V_i}{V_f}\right)^{\gamma-1}\\
\end{align*}
